\section{Hermitian line bundles}

Let \(K\) be a number field with ring of integers \(\calO_K\).
Let \(\calX\) be an arithmetic variety over \(\Spec \calO_K\) of relative dimension \(n\).
\Yang{flat,separated,of finite type,}

\subsection{Definitions and examples}

    \begin{definition}\label{def:hermitian_line_bundles}
        A \emph{hermitian line bundle} \(\overline{\calL} = (\calL, \{\|\cdot\|_\sigma\}_{\sigma \in M_K^\infty})\) on \(\calX\) consists of
        \begin{itemize}
            \item a line bundle \(\calL\) on \(\calX\);
            \item for each embedding \(\sigma: K \hookrightarrow \bbC\) (equivalently, each infinite place \(\sigma \in M_K^\infty\)), 
                a smooth hermitian metric \(\|\cdot\|_\sigma\) on the complex line bundle \(\calL_\sigma(\bbC)\) over \(\calX_\sigma(\bbC)\), 
                which is invariant under the complex conjugation map.
        \end{itemize}
        \Yang{To be checked.}
    \end{definition}

    \begin{example}\label{eg:hermitian_O_1_on_P^n_Z}
        Let \(\calX = \bbP^n_\bbZ\).

        \Yang{To be continued.}
    \end{example}

    \begin{definition}\label{def:tensor_product_and_dual_of_hermitian_line_bundles}
        Let \(\overline{\calL}_1\) and \(\overline{\calL}_2\) be hermitian line bundles on \(\calX\).
        \begin{itemize}
            \item The \emph{tensor product} \(\overline{\calL}_1 \otimes \overline{\calL}_2\) is defined as the line bundle \(\calL_1 \otimes \calL_2\) on \(\calX\) 
                equipped with the metrics \(\|s_1 \ten s_2\|_{\sigma} = \|s_1\|_{\sigma, 1} \cdot \|s_2\|_{\sigma, 2}\) on \((\calL_1 \otimes \calL_2)_\sigma(\bbC)\)
            \item The \emph{dual} \(\overline{\calL}_1^\vee\) is defined as the dual line bundle \(\calL_1^\vee\) on \(\calX\) 
                equipped with the dual metrics \(\|\cdot\|_{\sigma, 1}^\vee\) on \((\calL_1^\vee)_\sigma(\bbC)\) for each \(\sigma \in M_K^\infty\).
        \end{itemize}
        \Yang{To be checked.}
    \end{definition}

    \begin{definition}\label{def:pullback_of_hermitian_line_bundles}
        Let \(f: \calY \to \calX\) be a morphism of arithmetic varieties over \(\Spec \calO_K\).
        Let \(\overline{\calL} = (\calL, \{\|\cdot\|_\sigma\}_{\sigma \in M_K^\infty})\) be a hermitian line bundle on \(\calX\).
        The \emph{pullback} \(f^* \overline{\calL}\) is defined as the line bundle \(f^* \calL\) on \(\calY\)
        equipped with the metrics \(\|s\|_{\sigma}' = \|f_\sigma^* s\|_{\sigma}\) on \((f^* \calL)_\sigma(\bbC)\) for each \(\sigma \in M_K^\infty\),
        where \(f_\sigma: \calY_\sigma(\bbC) \to \calX_\sigma(\bbC)\) is the induced morphism of complex manifolds.
        \Yang{To be checked.}
    \end{definition}


    \begin{definition}\label{def:H^0_of_hermitian_line_bundles}
        Let \(\overline{\calL} = (\calL, \{\|\cdot\|_\sigma\}_{\sigma \in M_K^\infty})\) be a hermitian line bundle on \(\calX\).
        The set of \emph{small sections} of \(\overline{\calL}\) is defined as
        \[ H^0(\calX, \overline{\calL}) := \{ s \in H^0(\calX, \calL) : \|s\|_{\sigma} \leq 1 \text{ for all } \sigma \in M_K^\infty \}. \]
        \Yang{To be checked.}
    \end{definition}

    \begin{proposition}\label{def:H^0_of_hermitian_lb_is_finite}
        The set \(H^0(\calX, \overline{\calL})\) is finite.
    \end{proposition}

    \begin{definition}\label{def:h^0_and_volume_of_hermitian_line_bundles}
        Let \(\overline{\calL}\) be a hermitian line bundle on \(\calX\).
        We set 
        \[ h^0(\calX, \overline{\calL}) := \log \# H^0(\calX, \overline{\calL}). \]
        The \emph{volume} of \(\overline{\calL}\) is defined as
        \[ \vol(\overline{\calL}) := \limsup_{m \to \infty} \frac{h^0(\calX, \overline{\calL}^{\otimes m})}{m^{n+1}/(n+1)!}. \]
    \end{definition}